Precise predictions for same-sign W-boson scattering at the LHC

### 2018-03-05 Draft/shower.tex
aded shower_scale discussion

The first observable we investigate is the exclusive jet multiplicity, shown in Fig.~\ref{fig:PSnjet}. Looking at the LO+PS predictions, one can appreciate that the
main effects are driven by the parton shower that is employed ({\sc Herwig++/7} or {\sc Pythia8}), with the clear tendency of producing more radiation for the latter,
leading to higher jet multiplicities. Difference among tools that employ the same parton shower are typically smaller, and can be traced back to different values of the
initial scale of the parton shower.\MP{More details/comments there?}
The main effect of NLO corrections for this (rather inclusive) observable is to stabilise the predictions for the two-jet bin, where discrepancies
among tools are reduced to about $10\%$. For the three-jet bin, which is described only at LO accuracy, differences among tools remain large: the largest rate is predicted by
{\sc MG5\_aMC}, while the smallest rate is predicted by the {\sc Powheg-Box}, both matched to {\sc Pythia8}. Despite the fact that the same parton shower is employed, the way emissions are treated
is different among the two tools. In particular, for the {\sc Powheg-Box}, the first emission is generated with an internal Sudakov form factor (the
prediction dubbed {\sc Powheg-no shower} corresponds to stopping after the first emission), while for {\sc MG5\_aMC} there is an
interplay between the real-emission matrix element and the shower emission.

>>>>

The first observable we investigate is the exclusive jet multiplicity, shown in Fig.~\ref{fig:PSnjet}. Looking at the LO+PS predictions, one can appreciate that the
main effects are driven by the parton shower that is employed ({\sc Herwig++/7} or {\sc Pythia8}), with the clear tendency of producing more radiation for the latter,
leading to higher jet multiplicities. Difference among tools that employ the same parton shower are typically smaller, and can be traced back to different values of the
initial scale of the parton shower (the {\tt scalup} entry of the LHE file). This event-by-event number corresponds 
to the maximum hardness (translated into the shower evolution variable) of the radiation that 
can be generated by the shower. \footnote{At LO, the choice of such a scale is arbitrary and usually driven by common sense, 
as it is the case for the factorization and renormalization scales.
    At NLO, one has the freedom to change the shower scale without losing formal NLO accuracy within the {\sc MC@NLO} matching, 
    provided the Monte Carlo counterterms are also consistently
updated. In the {\sc Powheg} matching, the shower scale of the so-called $\tilde B$ events is fixed to the transverse momentum of the radiation 
generated by the {\sc Powheg} Sudakov, while it can be changed in the remnants events.}
The main effect of NLO corrections for this (rather inclusive) observable is to stabilise the predictions for the two-jet bin, where discrepancies
among tools are reduced to about $10\%$. For the three-jet bin, which is described only at LO accuracy, differences among tools remain large: the largest rate is predicted by
{\sc MG5\_aMC}, while the smallest rate is predicted by the {\sc Powheg-Box}, both matched to {\sc Pythia8}. Despite the fact that the same parton shower is employed, the way emissions are treated
is different among the two tools. In particular, for the {\sc Powheg-Box}, the first emission is generated with an internal Sudakov form factor (the
prediction dubbed {\sc Powheg-no shower} corresponds to stopping after the first emission), while for {\sc MG5\_aMC} there is an
interplay between the real-emission matrix element and the shower emission.
